\documentclass[aasms,12pt]{article}
\usepackage{natbib}
\setlength{\bibsep}{0pt plus 0.3ex}
\usepackage{sectsty}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage[skip=2pt,font=small]{caption}
\captionsetup{width=\textwidth}


%\usepackage{titlesec}
%
%\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
%\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
%\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}


\sectionfont{\normalsize}
\usepackage{fullpage}

%\usepackage[margin=1in]{geometry}

%\citestyle{aa}
\newcommand{\sol}{\ensuremath{\odot}}


\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}




\begin{document}
\begin{center}
   \large\textbf{Timeline of Graduate Studies}\\
   \vspace{0.4cm}
   \large{Evan Anders}\\
   \normalsize\textit{Department of Astrophysical and Planetary Sciences}\\
   \normalsize\textit{University of Colorado at Boulder}\\
\end{center}

\paragraph{Fall 2014 - Spring 2015:} Began graduate studies, and worked as a 
Teaching Assistant.
\vspace{-0.4cm}
\paragraph{Summer 2015:} Began work as a graduate Research Assistant with
	Dr. Benjamin P. Brown. \emph{Awarded CU Boulder's 3-year George Ellery Hale
	Graduate Student Fellowship}.

\vspace{-0.4cm}
\paragraph{Fall 2015:} Hale fellowship funding began.

\vspace{-0.4cm}
\paragraph{January 2016:} Completed department qualifier Comprehensive Exam I with
highest marks in cohort.

\vspace{-0.4cm}
\paragraph{Spring-Summer 2016:} Studied fundamental compressible, stratified convection
simulations.

\vspace{-0.4cm}
\paragraph{Fall 2016:} Passed second and final departmental Ph.D. qualifier, Comprehensive
Exam II. This exam was essentially a master's thesis defense.

\vspace{-0.4cm}
\paragraph{Spring 2017:} Improved work from comprehensive exam II and submitted it to Physical
Review Fluids (published in Summer 2017).  Worked on a side project analyzing stellar flares
on flare star YZ CMi, but decided to return to convection work for thesis.  
Finished graduate coursework.

\vspace{-0.4cm}
\paragraph{Summer - Fall 2017:}  Started two projects in convection: one studying internally heated,
stratified convection, and another studying how to use boundary value problems (BVPs) to fast-forward
convective solutions in order to save computational time.

\vspace{-0.4cm}
\paragraph{Spring 2018:} Submit paper on BVPs to referees (February 2018).  Continue
work on internally heated convection.  Getting married April 2018.

\vspace{-0.4cm}
\paragraph{Summer 2018:}  Finalize work on internally heated convection, 
submitting results to the Astrophysical Journal by end of summer.  \emph{End of
funding of Hale fellowship}.

\vspace{-0.4cm}
\paragraph{Fall 2018:} \emph{Start of proposed funding from NESSF}. Determine proper
atmospheric setup for simulations with realistic opacity and determine how to control
Mach number of these simulations.  Run first simulations with realistic opacities.

\vspace{-0.4cm}
\paragraph{Spring 2019:} Run final realistic opacity simulations, analyze and finalize
results on the effects of Mach number on these simulations.  Submit to The Astrophysical Journal.

\vspace{-0.4cm}
\paragraph{Summer-Fall 2019:} Determine proper atmospheric setup for simulations with
hydrogen ionization and recombination.  Run simulations and analyze data. Submit results
to the Astrophysical Journal.

\vspace{-0.4cm}
\paragraph{Spring 2020:} Write thesis, which will cover the work of the five published papers
above.  Defend thesis and graduate with Ph. D. in Astrophysical \& Planetary Sciences.

\end{document}
