\documentclass[aasms,12pt]{article}
\usepackage{natbib}
\setlength{\bibsep}{0pt plus 0.3ex}
\usepackage{sectsty}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage[skip=2pt,font=small]{caption}
\captionsetup{width=\textwidth}


%\usepackage{titlesec}
%
%\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
%\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
%\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}


\sectionfont{\normalsize}
\usepackage{fullpage}

%\usepackage[margin=1in]{geometry}

%\citestyle{aa}
\newcommand{\sol}{\ensuremath{\odot}}


\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}




\begin{document}
\begin{center}
   \large\textbf{Timeline of Graduate Studies}\\
   \vspace{0.4cm}
   \large{Evan H. Anders}\\
   \normalsize\textit{Advisor: Benjamin P. Brown}\\
   \normalsize\textit{Laboratory for Atmospheric and Space Physics (LASP) \& University of Colorado -- Boulder}\\
\end{center}

\paragraph{Fall 2014 - Spring 2015:} Began graduate studies and worked as a 
Teaching Assistant.
\vspace{-0.4cm}
\paragraph{Summer 2015:} Began work as a graduate Research Assistant with
	Dr. Benjamin P. Brown. \emph{Awarded CU Boulder's 3-year George Ellery Hale
	Graduate Student Fellowship}.

\vspace{-0.4cm}
\paragraph{Fall 2015:} \emph{Hale fellowship funding began}.

\vspace{-0.4cm}
\paragraph{January 2016:} Completed department qualifier Comprehensive Exam I with
highest marks in cohort.

\vspace{-0.4cm}
\paragraph{Spring-Summer 2016:} Began studies of stratified, compressible convection.

\vspace{-0.4cm}
\paragraph{Fall 2016:} Completed second and final departmental Ph.D. qualifier, Comprehensive
Exam II, which was essentially a master's thesis defense. Received ``High Pass'' distinction,
and advanced to Ph.D. candidacy.

\vspace{-0.4cm}
\paragraph{Spring 2017:} Improved work from Comprehensive Exam II and submitted it to Phys.
Rev. Fluids (Anders \& Brown 2017, Phys. Rev. Fluids).  Finished graduate coursework.

\vspace{-0.4cm}
\paragraph{Summer - Fall 2017:}  Conducted work on accelerated evolution project for
fast-forwarding convective solutions in order to save computational time (published in
Paper 2, below).

\vspace{-0.4cm}
\paragraph{Spring 2018:} Paper 2 (Anders, Brown, \& Oishi 2018, Phys. Rev. Fluids) published.
Got married April 2018.

\vspace{-0.4cm}
\paragraph{Summer 2018:}  Exploratory work on Kramer's opacity, as proposed in initial
application, and work on stratified, rotating convection. \emph{End of funding of Hale fellowship}.

\vspace{-0.4cm}
\paragraph{Fall 2018:} \textbf{\emph{Start of funding from NESSF18}}. Further exploratory work
on Kramer's opacity and thermals project. Submitted and
published paper 3 (Anders et al. 2019, ApJ) on rotating, stratified convection.

\vspace{-0.4cm}
\paragraph{Spring 2019:} Run thermals simulations, write thermals paper, submit
to The Astrophysical Journal by end of semester.

\vspace{-0.4cm}
\paragraph{Summer 2019 - Spring 2020:} Study ionizing convection as well as one of the other mini-projects
laid out in my renewal proposal, part 2. Submit a paper on one of these projects by end of
year 2019. Wrap up and submit other project by end of Spring or Summer 2020.

\vspace{-0.4cm}
\paragraph{Spring - Summer 2020:} Write and defend thesis and graduate with Ph. D. in Astrophysical \& Planetary Sciences.

\end{document}
